% notes.tex
% My scratch notes — no preamble
Just some random text, code, or half-written LaTeX.


Per Springer:

Book Structure
To guarantee a smooth publication process and a seamless transformation of your manuscript into the final layout and various electronic platforms, the manuscript needs to be structured as follows:

FRONT MATTER
- Title page*
    - Dedication
    - Foreword
    - Preface
    - Acknowledgments
    - About the book/conference
- Table of Contents*
    - About the Author (for authored books)
    - About the Editor / List of Contributors
    - List of Abbreviations
    - List of Figures and/or tables
*The title page and table of contents must appear in the manuscript's front matter, while all other sections listed above are optional.

Note that the above order is not flexible. They have defined this order as their house style and optimized their publication process to follow it strictly.

TITLE PAGE
Include all author and editor names, their affiliations and ORCID, the book title, and the subtitle. Ensure that the sequence of the author names is correct and the title of your book is final when you submit the manuscript.

Once the manuscript has been delivered to Production, changes to title, subtitle, or authorship are no longer possible.

FOREWORD
If you intend to include a foreword, please submit it with the manuscript.
- A foreword is usually written by an authority in the subject and serves as a recommendation for the book.
- The name of the forward's contributor is always given at the end of the foreword; affiliations and titles are generally not included, but the data and place of writing may be.

PREFACE
The preface should be about the book and it should stimulate interest in the book. Why it is important, why it was written, who it is for.
- The Preface should not be an introduction to the subject matter of the book. The Introduction does not belong in the front matter, but should appear as the first chapter.
- A preface should not contain a reference list.
- Acknowledgment of support or assistance in preparing the book can be included as the last paragraph(s) of the preface.
- If the acknowledgment is longer than one page, start a separate page with the heading "Acknowledgments."

TABLE OF CONTENTS
- Front matter material is not listed in the table of contents.
- List all parts, chapters, and back matter material (e.g., an index) in their final sequence.
- If your chapters are numbered, use Arabic numerals and number the chapters consecutively throughout the book (Chapter 1, Chapter 2, etc.), i.e., do not stat anew with each part. The introductory chapter must be listed as Chapter 1, if your chapters are numbered. Please do not use subchapters.
- In authored books they present two heading levels under the main chapter titles. In edited books, they present the chapter titles and the chapter author names.
- If there are parts, use Roman numerals for parts (Part I, Part II, etc.). Parts consist of a short title and can contain a short introductory text (optional).
- Do not use subparts.

LIST OF ABBREVIATIONS
- A list of abbreviations and/or symbols is optional, but it may be very helpful if numerous abbreviations are scattered throughout the text.























