\chapter{Security Hardening Guides and Best Practices}

\section{Hardening Guide Collection}

\subsubsection{1. CIS Benchmarks}
Community-developed, consensus-based security configuration guides for 100 technologies-operating systems, cloud, network devices, databases, and more-often used as de facto industry standards. Access requires registration for downloads via their WorkBench portal.
\textit{URL: https://www.cisecurity.org/cis-benchmarks}  

\subsubsection{2. ANSSI Best Practices}
Guidelines published by ANSSI, the French National Cybersecurity Agency, offering security-hardening recommendations, such as \textit{"Best Current Practices for Acquiring and Using Domain Names"} and other architectural and administrative guidance.
\textit{\textbf{URL:} https://www.ssi.gouv.fr/en/ }
\textbf{NOTE:} This ANSSI site provides best practice documents and guidance in English.

\subsubsection{3. National Security Agency (NSA) Cybersecurity Advisories \& Guidance}
Another tool repository belonging to the NSAs central hub provides publicly available resources such as cybersecurity advisories, information sheets, technical guidance and frameworks that aid in the hardening of systems and networks so that defenders can better protect them against future cyberattacks.
\textit{\textbf{URL}:https://www.nsa.gov/press-room/cybersecurity-advisories-guidance/  }

\subsubsection{3. National Security Agency (NSA) Cybersecurity Resources for Cybersecurity Professionals \& NSA Cybersecurity Publications}
A broader NSA repository of cybersecurity-related materials that include guides, info sheets, infographics, and archives, targeted at cybersecurity professionals. Many publications are listed and accessible via the \textit{Resources for Cybersecurity Professionals} page.
\textit{URL: https://nsacyber.github.io/publications.html}  

\subsubsection{4. US Department of Defense (DoD) Security Technical Implementation Guides (STIGs) \& Security Readiness Guides (SRGs)}
Part of the United States Cyber Command Division (USCYBERCOMMAND), DoD DISA publishes Security Technical Implementation Guides (STIGs) and Security Readiness / Requirements Guides (SRGs). Not only do these guides harden military and government-owned or leased systems, but they are made publicly available for civilians seeking guidance to better harden their assets by using these industry-accepted processes and specifications.
\textit{\textbf{URL:} https://public.cyber.mil/stigs/} 

OpenSCAP Security Policies